dendro

### 2017-05-26 analysis/analysis_chronologies.Rmd
update file and render

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
# library("detrendeR")
library("pander")
source(paste0(getwd(), '/script/R/bai_piovesan.R'))
source(paste0(getwd(), '/script/R/rw_byTree.R'))
source(paste0(getwd(), '/script/R/chrono_bai.R'))
source(paste0(getwd(), '/script/R/suaviza_cronos.R'))
```

@@

@@

```{r}
# Get summary ring-width series
sj_summ <- summary(sj)

@@

# Subbet datasets 
sj_cor <- sj[which(! colnames(sj) %in% (id_cores_no_bark))]
sj_sin <- sj[which(colnames(sj) %in% (id_cores_no_bark))]
```

@@

```{r}
compete <- read.csv(file=paste0(di, '/data_raw/dendro_competence.csv'), header=TRUE, sep=',')

@@

# remove diamm of cores without bark 
diam_cores_sj <- diam_cores %>% filter(! id_cores %in% id_cores_no_bark)
```

```{r}
rwl.report(sj_cor)

@@

```{r}
set.seed(1234)
serie <- sample(colnames(b_test_dplR),1)

@@

```{r, eval=FALSE, echo=FALSE}
# BAI dplR
baisj <- bai.out(rwl = sj_cor, diam = diam_cores_sj)

@@

```{r}

@@

```{r}
# tes plots

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
# library("detrendeR")
library("pander")
```

@@

```{r}
source(paste0(di, 'script/R/bai_piovesan.R'))
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/chrono_bai.R'))
source(paste0(di, 'script/R/suaviza_cronos.R'))
```

@@

# Get summary ring-width series
sj_summ <- summary(sj)

@@

# Subbet datasets 
sj_cor <- sj[which(! colnames(sj) %in% (id_cores_no_bark))]
sj_sin <- sj[which(colnames(sj) %in% (id_cores_no_bark))]

@@

compete <- read.csv(file=paste0(di, '/data_raw/dendro_competence.csv'), header=TRUE, sep=',')

@@

# remove diamm of cores without bark 
diam_cores_sj <- diam_cores %>% filter(! id_cores %in% id_cores_no_bark)

rwl.report(sj_cor)

@@

set.seed(1234)
serie <- sample(colnames(b_test_dplR),1)

@@

# BAI dplR
baisj <- bai.out(rwl = sj_cor, diam = diam_cores_sj)

@@

@@

# tes plots
